A Multi-telescope Campaign on \frb: Implications for the FRB Population

### 2017-04-26 repeater-vladata.tex
got jim comments in

\title{The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories. Only one VLA burst was detected by another observatory, the Arecibo Observatory at 1.4~GHz. We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law. We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a systematic random to the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1. This rate is broadly consistent with models of FRBs from young magnetars or pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.

@@

Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}. The large measured DM implied that FRBs originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out 
cataclymic models for this source \citep{2016Natur.531..202S}. The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).

Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec. Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}. The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. At this distance, \frb\ is orders of magnitude more luminous than any other millisecond radio transient. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.

Many new models of FRB origin have been been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}. The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is not a prediction of models that scale with stellar mass or star formation \citep{2017arXiv170400022N}. These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.

@@

In Section \ref{sec:obs}, we describe the multi-telescope observing campaign and a refined analysis of the nine VLA bursts. Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes and show that burst spectra cannot be modeled with a single spectral index. We then model the dynamic spectra to characterize the burst spectra, energies, and dispersion properties. Section \ref{sec:disc} discusses the properties of \frb\ bursts and its impact on inferences about the birth rate of FRB sources and strategies to find and/or localize new FRBs.

@@

Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \software{\url{https://github.com/caseyjlaw/FRB121102}}. Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}. Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

@@

Observations in August and September were searched by a prototype version of \rf\ \citep[see \url{http://realfast.io};][]{2017AAS...22933002L}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \software{\emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and \citet{2015ApJ...807...16L}.}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra and has an accuracy of about 10\%.

Burst detections and localizations were made within hours of data being recorded. The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ``quasi real-time''. For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image. We empirically identified S/N thresholds of 6.4 and 7.4 as useful to capture data quality statistics and candidates for inspection, respectively. The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed (and computationally intensive) candidate visualization that includes an image and spectrum. All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.

@@

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{cc|rrr|ccrrrr}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

@@

We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square temporal width (W). The inter-channel amplitude modulation was ignored in the model.

@@

% ** confusion as to whether inter-channel modulation is signal or noise ** jim also to do noise analysis **

@@

% ** expand on implication of spectral envelope in scintillation models **

@@

Assuming that \frb\ is representative of the FRB population, we calculate a volumetric birth rate of FRB sources that does not depend on telescope sensitivity. We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$. This rate is broadly consistent with models of FRBs from young magnetars or pulsars if the typical FRB repeats on the order of $10^3$\ times over its lifetime.

@@

\appendix

% ** add mjd colum **
% ** use footnotes instead of last two cols? **

\section{Table of Observations}

\startlongtable
\begin{deluxetable*}{lcccccc}
\small
\tablecaption{Table of Observations \label{tab:obs}}
%\centering
%\begin{tabular}{lcccccc}
\startdata
Day & Start time & Duration & Band & VLA Detections & Other Coverage & Other Detections \\
(yyyy-mm-dd; UT) & (hh:mm:ss; UT) & (minutes) & & & &  \\ \hline
2015-11-25 & 3:25:29 & 60 & 1.4~GHz & 0 &  & \\
2015-12-01 & 5:31:31 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-03 & 2:53:57 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-05 & 4:45:44 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-07 & 4:37:50 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-09 & 9:29:25 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-11 & 9:22:27 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-13 & 9:13:7 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-15 & 9:6:16 & 60 & 1.4~GHz & 0 &  &  \\
2015-12-17 & 8:57:51 & 60 & 1.4~GHz & 0 &  &  \\
2016-04-25 & 15:39:33 & 42 & 3~GHz & 0 &  &  \\
2016-04-26 & 21:49:35 & 15 & 3~GHz & 0 &  &  \\
2016-04-30 & 19:14:46 & 60 & 3~GHz & 0 &  &  \\
2016-05-01 & 18:8:21 & 60 & 3~GHz & 0 &  &  \\
2016-05-03 & 22:53:26 & 60 & 3~GHz & 0 &  &  \\
2016-05-04 & 22:50:30 & 60 & 3~GHz & 0 &  &  \\
2016-05-06 & 18:25:12 & 60 & 3~GHz & 0 &  &  \\
2016-05-07 & 19:34:13 & 60 & 3~GHz & 0 &  &  \\
2016-05-08 & 19:30:20 & 60 & 3~GHz & 0 &  &  \\
2016-05-13 & 17:12:48 & 135 & 3~GHz & 0 &  &  \\
2016-05-14 & 17:14:11 & 135 & 3~GHz & 0 &  &  \\
2016-05-15 & 17:15:26 & 135 & 3~GHz & 0 &  &  \\
2016-05-16 & 16:59:52 & 135 & 3~GHz & 0 &  &  \\
2016-05-20 & 16:45:46 & 135 & 3~GHz & 0 &  &  \\
2016-05-21 & 16:44:6 & 135 & 3~GHz & 0 &  &  \\
2016-05-22 & 16:43:53 & 135 & 3~GHz & 0 &  &  \\
2016-05-23 & 16:44:11 & 135 & 3~GHz & 0 &  &  \\
2016-05-27 & 16:29:34 & 135 & 3~GHz & 0 &  &  \\
2016-08-23 & 17:26:28 & 54 & 3~GHz & 1 &  &  \\
2016-09-02 & 15:52:17 & 54 & 3~GHz & 2 &  &  \\
2016-09-07 & 10:14:50 & 120 & 3~GHz & 1 &  &  \\
2016-09-08 & 10:14:40 & 120 & 3~GHz & 0 &  &  \\
2016-09-10 & 9:59:36 & 120 & 3~GHz & 0 &  &  \\
2016-09-11 & 9:59:49 & 120 & 3~GHz & 0 &  &  \\
2016-09-12 & 9:15:19 & 120 & 3~GHz & 1 & AMI-LA &  \\
2016-09-13 & 9:23:59 & 120 & 3~GHz & 0 &  &  \\
2016-09-14 & 9:20:23 & 120 & 3~GHz & 1 & Arecibo, AMI-LA &  \\
2016-09-15 & 9:16:29 & 120 & 3~GHz & 1 &  &  \\
2016-09-16 & 9:11:23 & 120 & 3~GHz & 0 &  &  \\
2016-09-17 & 8:59:20 & 120 & 3~GHz & 1 & Arecibo, Effelsberg, AMI-LA & Arecibo \\
2016-09-18 & 8:59:27 & 120 & 3~GHz & 1 & Arecibo, Effelsberg, AMI-LA &  \\
2016-09-19 & 8:44:32 & 120 & 3~GHz & 0 &  &  \\
2016-09-20 & 8:44:33 & 120 & 3~GHz & 0 &  &  \\
2016-09-20 & 17:19:3 & 120 & 6~GHz & 0 &  &  \\
2016-09-21 & 9:13:57 & 120 & 6~GHz & 0 &  &  \\
2016-09-22 & 9:12:24 & 120 & 6~GHz & 0 &  &  \\
\enddata
\tablecomments{Arecibo, Effelsberg, and AMI-LA observations were conducted at 1.4, 4.5, and 15~GHz, respectively.}
%\end{tabular}
%\tablenotetext{a}{}
%\label{tab:obs}
\end{deluxetable*}

@@

We thank Liam Connor for useful feedback and the VLA staff for their support of \rf\ development. We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).

>>>>

\title{A Multi-telescope Campaign on \frb: Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories. Only one VLA burst was detected by another observatory, the Arecibo Observatory at 1.4~GHz. We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law. We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg. We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a systematic random to the estimate of DM by up to 1\%. We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime. This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.

@@

Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}. The largest measured DMs imply that FRBs originate outside of our Galaxy, potentially at cosmological distances, and are orders of magnitude more luminous than pulses from Galactic pulsars \citep{2013Sci...341...53T}. There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C}. In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}. The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).

Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec. Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}. The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.

Many new models for the origin of FRBs have been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}. The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is not a prediction of models that scale with stellar mass or star formation \citep{2017arXiv170400022N}. These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.

@@

In Section \ref{sec:obs}, we describe the multi-telescope observing campaign and a refined analysis of the nine VLA bursts. Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes and confirm that burst spectra cannot be modeled with a single spectral index. We then model the dynamic spectra to characterize the burst spectra, energies, and dispersion properties. Section \ref{sec:disc} discusses the properties of \frb\ bursts and its impact on inferences about the birth rate of FRB sources and strategies to find and/or localize new FRBs.

@@

Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}. Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}. Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

% ** add mjd colum **

\startlongtable
\begin{deluxetable}{lcccc}
\small
\tablecaption{Table of VLA Observations \label{tab:obs}}
%\centering
%\begin{tabular}{lcccccc}
\startdata
Day & Start time & Duration & Freq. & Bursts \\% & Other Coverage & Other Detections \\
(yyyy-mm-dd) & (hh:mm:ss) & (min) & (GHz) & \\ \hline
2015-11-25 & 3:25:29 & 60 & 1.4 & 0 \\
2015-12-01 & 5:31:31 & 60 & 1.4 & 0 \\
2015-12-03 & 2:53:57 & 60 & 1.4 & 0 \\
2015-12-05 & 4:45:44 & 60 & 1.4 & 0 \\
2015-12-07 & 4:37:50 & 60 & 1.4 & 0 \\
2015-12-09 & 9:29:25 & 60 & 1.4 & 0 \\
2015-12-11 & 9:22:27 & 60 & 1.4 & 0 \\
2015-12-13 & 9:13:7 & 60 & 1.4 & 0 \\
2015-12-15 & 9:6:16 & 60 & 1.4 & 0 \\
2015-12-17 & 8:57:51 & 60 & 1.4 & 0 \\
2016-04-25 & 15:39:33 & 42 & 3 & 0  \\
2016-04-26 & 21:49:35 & 15 & 3 & 0  \\
2016-04-30 & 19:14:46 & 60 & 3 & 0  \\
2016-05-01 & 18:8:21 & 60 & 3 & 0  \\
2016-05-03 & 22:53:26 & 60 & 3 & 0  \\
2016-05-04 & 22:50:30 & 60 & 3 & 0  \\
2016-05-06 & 18:25:12 & 60 & 3 & 0  \\
2016-05-07 & 19:34:13 & 60 & 3 & 0  \\
2016-05-08 & 19:30:20 & 60 & 3 & 0  \\
2016-05-13 & 17:12:48 & 135 & 3 & 0  \\
2016-05-14 & 17:14:11 & 135 & 3 & 0  \\
2016-05-15 & 17:15:26 & 135 & 3 & 0  \\
2016-05-16 & 16:59:52 & 135 & 3 & 0  \\
2016-05-20 & 16:45:46 & 135 & 3 & 0  \\
2016-05-21 & 16:44:6 & 135 & 3 & 0  \\
2016-05-22 & 16:43:53 & 135 & 3 & 0  \\
2016-05-23 & 16:44:11 & 135 & 3 & 0  \\
2016-05-27 & 16:29:34 & 135 & 3 & 0  \\
2016-08-23 & 17:26:28 & 54 & 3 & 1  \\
2016-09-02 & 15:52:17 & 54 & 3 & 2  \\
2016-09-07 & 10:14:50 & 120 & 3 & 1  \\
2016-09-08 & 10:14:40 & 120 & 3 & 0  \\
2016-09-10 & 9:59:36 & 120 & 3 & 0  \\
2016-09-11 & 9:59:49 & 120 & 3 & 0  \\
2016-09-12 & 9:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
2016-09-13 & 9:23:59 & 120 & 3 & 0  \\
2016-09-14 & 9:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
2016-09-15 & 9:16:29 & 120 & 3 & 1  \\
2016-09-16 & 9:11:23 & 120 & 3 & 0  \\
2016-09-17 & 8:59:20 & 120 & 3 & 1\tablenotemark{a,b,*,c} \\ 
2016-09-18 & 8:59:27 & 120 & 3 & 1\tablenotemark{a,b,c} \\
2016-09-19 & 8:44:32 & 120 & 3 & 0  \\
2016-09-20 & 8:44:33 & 120 & 3 & 0  \\
2016-09-20 & 17:19:3 & 120 & 6 & 0  \\
2016-09-21 & 9:13:57 & 120 & 6 & 0  \\
2016-09-22 & 9:12:24 & 120 & 6 & 0  \\
\enddata
\tablecomments{Times are in UT. Frequency is the approximate center of the bandwidth.}
\tablenotetext{a}{AMI-LA coverage at 15~GHz.}
\tablenotetext{b}{Arecibo coverage at 1.4~GHz.}
\tablenotetext{*}{Arecibo detection at 1.4~GHz.}
\tablenotetext{c}{Effelsberg coverage at 4.5~GHz.}
%\end{tabular}
%\tablenotetext{a}{}
%\label{tab:obs}
\end{deluxetable}

@@

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io} and \citep{2017AAS...22933002L}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}. Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$. Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration. A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra and has an accuracy of about 10\%.

Burst detections and localizations were made within 5--10 hours of data being recorded. The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ``quasi real-time''. For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image. We empirically identified S/N thresholds of 6.4 and 7.4 as useful to capture data quality statistics and candidates for inspection, respectively. The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed (and computationally intensive) candidate visualization that includes an image and spectrum. All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.

@@

\begin{table*}
\caption{Properties of \frb\ Bursts at 3~GHz}
\centering
\begin{tabular}{cc|rrr|ccrrrr}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

@@

We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency). We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled prior to dispersion correction. The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, width), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM). Finally, the pulses were assumed to have an intrinsically square temporal width (parameter W). This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid. The inter-channel amplitude modulation was ignored in the model.

@@

% ** confusion as to whether inter-channel modulation is signal or noise ** jim also to do noise analysis **
% ** could quantify deviations from Gaussian model relative to noise. An SNR relative to envelope.

@@

% ** expand on implication of spectral envelope in context of scintillation interpretation of FRB brightness **

@@

Assuming that \frb\ is representative of the FRB population, we calculate a volumetric birth rate of FRB sources that does not depend on telescope sensitivity. We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$. This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times over its lifetime.

@@

@@

We thank the VLA staff for their support of \rf\ development and Liam Connor for useful feedback. We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).

\software{\emph{rtpipe}, \emph{realfast}}
